R Notebook

### 2021-03-11 eda.Rmd
Work on bulk_purchase EDA

```{r}
ggplot(small_ppm, aes(x=ppm, fill=bulk_purchase, color=bulk_purchase)) +
    geom_histogram(position="identity", alpha=0.5)
```

>>>>

```{r}
ggplot(small_ppm, aes(x=bulk_purchase, y=ppm)) + geom_boxplot()
```

It looks like bulk purchases are generally associated with cheaper prices. But are these differences in means significant? We may apply the t-test because the CLT kicks in for these large groups

```{r}
t.test(ppm ~ bulk_purchase, data = small_ppm)
```

So bulk purchase looks to be a significant predictor *if* we exclude the extreme ppm values
